Drought-sensitive trees survive on deep water access in a tropical forest community

### 2020-07-10 manuscript.rmd
edited figure captions to add inline code

```{r comm-plc-curves, eval = TRUE, echo = FALSE, message = FALSE, fig.align ='center', out.width = "30%", fig.pos = 'H', fig.cap = paste("\\label{lab-comm-plc-curves} Modelled standardized 'Vulnerability curves' for  $K_{x, Leaf}$ vs. $\\Psi_{x, Leaf}$ at community-scale based on communit-scale data on $WSG$ & $LMA$ and their relationships with vulnerability curve parameters measured for a few species. Each line represents a species, color coded by $WSG$.")}
knitr::include_graphics(file.path("figures/PhenoDemoTraitsPsi/kmax_by_psi/Leaf/kmax_by_psi_color_by_Wood Specific Gravity_predicted_AB.jpeg"))
```

@@

```{r erd-iso, eval = TRUE, echo = FALSE, message = FALSE, fig.align ='center', out.width = "80%", fig.pos = 'H', results = "asis", fig.cap = "\\label{lab-erd-iso}Modelled Effective Rooting Depth (ERD; mean $\\pm$ 1SE; m) versus dry season stable isotopic concentration $\\delta$^2^H (mean $\\pm$ (add error); ‰) for seven canopy species from Barro Colorado Island (data from [@Meinzer:1999]"}
knitr::include_graphics(file.path("figures/PhenoDemoTraitsPsi/psi.corr_best.depth_xylem_sap_deltaD_phenology_Meinzer_gr.Psi.VPD.jpeg"))
```

@@

```{r erd-hyd, eval = TRUE, echo = FALSE, message = FALSE, fig.align ='center', out.width = "60%", fig.pos = 'H', results = "asis", fig.cap = paste0("\\label{lab-erd-hyd}Modelled Effective Rooting Depth (ERD; mean $\\pm$ (add error) in m) versus hydraulic propertiese for seven large, canopy species found on Barro Colorado Island. *R*^2^ and *P*-values are given in panel insets."}
knitr::include_graphics(file.path("figures/PhenoDemoTraitsPsi/Select_traits_depth.jpeg"))
```

@@

```{r erd-time, eval = TRUE, echo = FALSE, message = FALSE, fig.align ='center', out.width = "40%", fig.pos = 'H', results = "asis", fig.cap = "\\label{lab-erd-time}Species modelled Effective Rooting Depth (ERD; mean $\\pm$ (add error) in m) versus time spent below critical hydraulic threhold--the number of days for which $\\Psi_{x, z}$ was below $\\Psi_{80,Leaf}$ over 1990-2015, where z is the soil depth matching species ERD--for xx canopy species found on Barro Colorado Island. (Are *R*^2^ and *P*-values needed here?)"}
knitr::include_graphics(file.path("figures/PhenoDemoTraitsPsi/mean_mfac vs. rdi.gr.jpeg"))
```

@@

>>>>

```{r comm-plc-curves, eval = TRUE, echo = FALSE, message = FALSE, fig.align ='center', out.width = "30%", fig.pos = 'H', results = "asis", fig.cap = paste0("\\label{lab-comm-plc-curves} Modelled standardized 'Vulnerability curves' ($K_{x, Leaf}$ vs. $\\Psi_{x, Leaf}$) at community-scale (", nrow(data.model.AB$sp)," species) based on species data on $WSG$ & $LMA$ and their relationships with vulnerability curve parameters measured on ", sp.soft.filled$AB.data.model," species. Each line represents a species, color coded by $WSG$.")}
knitr::include_graphics(file.path("figures/PhenoDemoTraitsPsi/kmax_by_psi/Leaf/kmax_by_psi_color_by_SG100C_AVG_predicted_AB.jpeg"))
knitr::include_graphics(file.path("figures/PhenoDemoTraitsPsi/kmax_by_psi/Leaf/kmax_by_psi_color_by_LMALAM_AVD_predicted_AB.jpeg"))
```

@@

```{r erd-iso, eval = TRUE, echo = FALSE, message = FALSE, fig.align ='center', out.width = "80%", fig.pos = 'H', results = "asis", fig.cap = paste0("\\label{lab-erd-iso}Modelled Effective Rooting Depth (ERD; mean $\\pm$ 1SE; m) versus dry season stable isotopic concentration $\\delta$^2^H (mean $\\pm$ (add error); ‰) for ", length(subset(ml.rsq.combine.sub, source == "Meinzer et al.1999 Fig. 4" & corr.func == "gr.Psi.VPD")$sp)," canopy species from Barro Colorado Island (data from [@Meinzer:1999]")}
knitr::include_graphics(file.path("figures/PhenoDemoTraitsPsi/psi.corr_best.depth_xylem_sap_deltaD_phenology_Meinzer_gr.Psi.VPD.jpeg"))
```

@@

```{r erd-hyd, eval = TRUE, echo = FALSE, message = FALSE, fig.align ='center', out.width = "60%", fig.pos = 'H', results = "asis", fig.cap = paste0("\\label{lab-erd-hyd}Modelled Effective Rooting Depth (ERD; mean $\\pm$ (add error) in m) versus hydraulic propertiese for seven large, canopy species found on Barro Colorado Island (Panama). *R*^2^ and *P*-values are given in panel insets."}
knitr::include_graphics(file.path("figures/PhenoDemoTraitsPsi/Select_traits_depth.jpeg"))
```

@@

```{r erd-time, eval = TRUE, echo = FALSE, message = FALSE, fig.align ='center', out.width = "40%", fig.pos = 'H', results = "asis", fig.cap = paste0("\\label{lab-erd-time} Modelled Species Effective Rooting Depth (ERD; mean $\\pm$ (add error) in m) versus time spent below critical hydraulic threhold--the number of days for which $\\Psi_{x, z}$ was below $\\Psi_{80,Leaf}$ over 1990-2015, where z is the soil depth matching species ERD--for ", ," canopy species found on Barro Colorado Island. (Are *R*^2^ and *P*-values needed here?)")}
knitr::include_graphics(file.path("figures/PhenoDemoTraitsPsi/mean_mfac vs. rdi.gr.jpeg"))
```

@@

```{r leaf-cover, eval = TRUE, echo = FALSE, message = FALSE, fig.align ='center', out.width = "40%", fig.pos = 'H', results = "asis", fig.cap = paste0("\\label{lab-leaf-cover} Seasonal variation in Leaf Cover Fraction for ", length(unique(sp.leaf_cover.for.model$sp[sp.leaf_cover.for.model$deciduousness != "Evergreen"]))," non-evergreen species at Barro Colorado Island. Leaf Cover Fraction for evergreen species (n = ", length(unique(sp.leaf_cover.for.model$sp[sp.leaf_cover.for.model$deciduousness == "Evergreen"])),") is assumed at 1 through the year.")}
knitr::include_graphics(file.path("figures/PhenoDemoTraitsPsi/leaf_fall/leaf.cover_BCI_single_panel_evergreensAt100.jpeg"))
```
